Speeding up decimal multiplication

### 2020-11-23 paper/paper.tex
Update

In the circumstances described above, one would believe,
we have no choice but to give up and accept the complexity --- after all,
much research has been dedicated to this problem;
if there were a simple solution, somebody would find it --- and perhaps
\textbf{mpdecimal} would use it.
After all, the case of six-step FFT with its
$2^k \times 2^{k+1}$ or $2^{k+1} \times 2^k$ matrices must be an important enough
application for a matrix transposition.

@@

Now, the case of inverse transform.
We now need to multiply each matrix element indexed $\langle i,j \rangle$
by $(\xi_N)^{-ij},$ then perform length-3 IDFT on each column; and also multiply everything by a
factor $\Phi.$

>>>>

In the circumstances described above, one would believe,
we have no choice but to give up and accept the complexity --- after all,
much research has been dedicated to this problem;
if there were a simple solution, somebody would find it --- and perhaps
\textbf{mpdecimal} would use it.
The case of six-step FFT with its
$2^k \times 2^{k+1}$ or $2^{k+1} \times 2^k$ matrices must be an important enough
application for a matrix transposition.

@@

Consider now the case of inverse transform.
We need to multiply each matrix element indexed $\langle i,j \rangle$
by $(\xi_N)^{-ij},$ then perform length-3 IDFT on each column; and also multiply everything by a
factor $\Phi.$
